Object-Oriented Internet - Azure Interoperability

### 2020-12-01 Latex/Manuscript.tex
Update Azure
#37 

> Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.

In the previous chapter it was said that "the embedded gateway is not derived from the middleware concept" (I've noted it in #43 too, so I guess it should be adjusted earlier?)

> Removed  "called telemetry"

Depending on the context this could be wrong as the azure docs specify various kinds of data including but not limited to telemetry. I think it's best to skip this part.

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication. This communication is transparent, i.e.~it is not data types aware allowing
any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, HTTPS.

Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated. It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services. In the gateway scenario, they can be mapped on each other or entirely independent. The \textit{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \textit{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \textit{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \textit{IoT\ Hub} service. The device proceeds to use the same attestation in \textit{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.

@@

In \textit{IoT\ Central} a CPS is represented as a set
of devices. The characteristics and behavior of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data (called telemetry) exchanged over the
wire with the CPS called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\textit{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
CPS. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
stacks. In any case, process data (telemetry) is transparently
transferred back-and-forth to the upper layer \textit{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textit{IoT\ Central} solution.

>>>>

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication [TODO: Reference]. This communication is transparent, i.e.~it is not data types aware allowing
any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.

Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated. It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services. In the gateway scenario, they can be mapped on each other or be entirely independent. The \textit{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \textit{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \textit{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \textit{IoT\ Hub} service. The device proceeds to use the same attestation in \textit{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.

@@

In \textit{IoT\ Central} a CPS is represented as a set
of devices. The characteristics and behavior of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data exchanged over the
wire with the CPS called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\textit{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
CPS. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT and HTTPS protocol
stacks. In any case, process data is transparently
transferred back-and-forth to the upper layer \textit{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textit{IoT\ Central} solution.
